---
title: "Baltimore Murals"
author: "Leanne Fortney"
date: "April 10, 2017"
output: html_document
---


```{r}
library(sf)                  
library(leaflet)            
library(scales)             
library(tidyverse)
library(cleanNLP)
library(ggmap)
```
```{r}
Baltimore_City_Murals <- read_csv("~/Desktop/School/Clio2/Baltimore City/Baltimore_Murals/Baltimore_Murals/Baltimore_City_Murals.csv",
     col_types =  cols( 
    location = col_character(),
    city = col_character(),
    state = col_character(),
    artistFirstName = col_character(),
    artistLastName = col_character(),
    YEAR = col_integer(),
    address = col_character()
))
```

```{r}
artists <- Baltimore_City_Murals %>% 
    select(-address) %>% 
    mutate(artist_name = paste(artistFirstName, artistLastName, sep = " ")) %>%
    mutate(site = paste(location, city, state, sep = ", "))
select(artists, artist_name, location)

coords <- geocode(artists$location, output = "latlona") 
address_coords <- bind_cols(artists, coords) 

address_coords %>% 
select(address_coords, artist_name, YEAR, lon, lat) %>% 

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(data = address_coords,
                   lng = ~lon, lat = ~lat,
                   color = "purple", weight = 1,
                   popup = ~paste(artist_name, '<br>', location))
```
```
In 1975, Baltimore City initiated a record of 

```{r Baltimore, echo=FALSE}

artists <- Baltimore_City_Murals %>% 
    select(-address) %>% 
    mutate(artist_name = paste(artistFirstName, artistLastName, sep = " ")) %>%
    mutate(site = paste(location, city, state, sep = ", "))

coords <- geocode(Baltimore_City_Murals$site, output = "latlona")
address_coords <- bind_cols(to_geocode, coords)

address_coords %>% 
  select(artist, location, lon, lat)


select(Baltimore_City_Murals, address, lon, lat) 


leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(data = address_coords,
                   lng = ~lon, lat = ~lat,
                   label = ~paste(artist),
                   radius = 10,
                   color = "purple", weight = 1,
                   popup = ~paste(artist, '<br>', address))

```

